---
---

---

# Results

Your RStudio results should look like the following. I've displayed the R code chunks before the results.

## Descriptives

First, let's get some descriptives of the data. Remember that `ID` is simply a case identifier and isn't important for this.

```{r descriptives, echo = TRUE, results='asis'}
library(summarytools)
descr(dfb, style = "rmarkdown")
```


## Scatterplot

Using the simple RStudio **plot** command:

```{r scatterplot, echo = TRUE}
plot(comm, peers,                         # plot the variables 
  xlab="Communication",                   # x axis label 
  ylab="Peer relationships")              # y axis label
  abline(lm(comm ~ peers))                # draw the trend line
```

Using the more enjoyable **ggplot2** command that provides a nicer looking scatterplot *and* confidence intervals around the trend line:

```{r ggplot2, echo = TRUE}
library(ggplot2)
ggplot(dfb, aes(x=comm, y=peers)) +
  geom_point(shape=1) +
  geom_smooth(method=lm)
```

## Correlations

Pearson's correlation coefficient: `r cor(comm, peers)`

```{r correlation, echo = TRUE}
cor(comm, peers)
```

## $ r^{2} $

To determine the $ r^{2} $ we'll need to examine the coefficients a bit more closely. It's easier if we create an object in RStudio to do just that:

```{r rsquared, echo = TRUE}
model1 <- lm(comm~peers)
summary(model1)
```
